\ProjectName{}: Data Imputation as a Query Optimization

### 2016-12-12 paper/examples.tex
add paper skeleton
paper: skeleton experiments
paper: Add to examples section

\section{Conclusion}

>>>>

\section{Examples}

Consider the case of an analyst looking to explore the sources and causes of
polling error in a presidential election. One hypothesis \cite{zukin2015s}
is that the rapid switch from landlines to cellphones has increased the
difficulty of contacting potential poll respondents. The analyst may
begin her analysis by comparing the polling error in a state with the
distribution of households with landlines, for the set of states for which
polling error was most pronounced. In order to probe deeply, the analyst
accesses a household-level survey of household characteristics that includes
whether the household has a landline. One such survey --- which will be
discussed further --- is the American Community Survey (ACS), conducted by the
US Census Bureau.

Surveys are rife with missing values due to non-response and other issues, and
the ACS is no exception. The missing values could be imputed in an expensive
operation\footnote{One would not necessarily want to impute the entire database once and
store the imputed values, as in many settings the imputation strategy would be
targeted for a specific question or domain.}, or the rows with missing values could be dropped entirely. With
ImputeDB, the analyst could impute the relevant subset of data on-the-fly,
achieving better performance without losing the information in the dropped
examples.

The analyst submits a query to ImputeDB which finds an optimized query plan.

\begin{verbatim}
SELECT polling.state, AVG(acs.TEL)
FROM polling, acs
WHERE polling.state = acs.ST
  AND polling.error > 50
GROUP BY polling.state
\end{verbatim}

\todo{explore a couple of plans generated, using dot visualizer}
